Evaluating the evidence of widespread maintenance of functional composition in vertebrate communities

### 2021-10-11 paper/manuscript.Rmd
significance statement.

We estimated general trends for each diversity metric using a linear mixed effects model with a random slope and intercept for each study and each time series nested within the study.
To test for trends within taxa, biome, and realm we also fit models with random slope and intercept effects for each one of these factors.
We obtained study-level estimates of temporal change from the Best Linear Unbiased Predictors (BLUPs) for each overall trend model with no additional covariates.
BLUP's provide an estimate for the conditional mean and variance of each level of a random effect from which we calculated 95% confidence intervals to determine significance of study-level slopes.
We assessed the impact of time series duration and start year on study-level trends using general linear models with duration and start year as predictors.
All models were executed using the *lme4* package in R and p-values were calculated using the *lmerTest* package [@bates2015; @rcoreteam2021].

>>>>

We estimated general trends for each diversity metric using a linear mixed effects model with a random slope and intercept for each study and each time series nested within the study.
To test for trends within taxa, biome, and realm we also fit models with random slope and intercept effects for each one of these factors.
We obtained study-level estimates of temporal change from the Best Linear Unbiased Predictors (BLUPs) for each overall trend model with no additional covariates.
BLUP's provide an estimate for the conditional mean and variance of each level of a random effect from which we calculated 95% confidence intervals to determine significance of study-level slopes.
We assessed the impact of time series duration and start year on study-level trends using general linear models with duration and start year as predictors.
All models were executed using the *lme4* package in R and p-values were calculated using the *lmerTest* package with a significance level of p \< 0.05 [@bates2015; @rcoreteam2021].
